Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-12 Scripts/Initial_Analysis.Rmd
Created top 5 map and circular plot. I think the map is better

# Create data
Top_map_data <- top_toe %>% 
  filter(tresh == selected_tresh,
         variable == "value") %>% 
  mutate(mean = mean-2000) %>%
  arrange(mean)

# -------------------------- #
# Call plot for both tresholds
# -------------------------- #
# tresh_list <- c("tresh_one","tresh_two")

  # Value Map
  World_map_part <- World_map_nemer %>% 
  filter(
    tresh ==  ,
    variable == "value"
  )

@@

>>>>

# Create data
Top_map_data <- top_toe %>% 
  filter(tresh == selected_tresh,
         variable == "value") # tried with catch but is quite the same

World_map_top <- World_map %>%
  full_join(Top_map_data,
            by = c("sau_fishing_entity")
  ) %>% 
  filter(!is.na(variable))

# These are regions without transboundary species
grey_land <- World_map %>% 
  filter(!sau_fishing_entity %in% Top_map_data$sau_fishing_entity) %>% 
  filter(!sovereignt %in% c("Antarctica"))

@@

  map <- ggplot(World_map_top) +
    geom_sf(
      aes(
        fill = mean #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    # geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    scale_fill_viridis("Average year of range shift",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       direction = -1
    ) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(legend.key.width = unit(5, "line")) +

    guides(
      fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

  ggsave(
    plot = map,
    "./Figures/top_toe_map.png",
    width = 10,
    height = 5,
    units = "in"
  )
